% @brief    LaTeX2e Resume for Oliver Zheng
\documentclass[margin,line]{resume}

%--------------
\begin{document}

\name{\Large Oliver Zheng}
\begin{resume}

	%------------------------------------------
	\section{\mysidestyle About}
	I am a software engineer interested in the networking and web-based
	products. I craft amazing experiences with meticulous design and solid
	engineering.

	%------------------------------------------
	\section{\mysidestyle Contact}
	(425) 440-1789
		\vspace{1mm}\\
	me@oliverzheng.com

	%--------------------------------------
	\section{\mysidestyle Expertise}
	Languages: C/C++, Python, C{\#}, PHP, Javascript, HTML, CSS, SQL
		\vspace{1mm}\\
	Frameworks: Node.js, Twisted, Django, Knockout.js, Ember.js
		\vspace{1mm}\\
	Platforms: Win32, Linux, Google App Engine, Azure, Heroku

	%----------------------------------------------
	\section{\mysidestyle Work History}

	\textbf{Facebook, Inc}, Seattle, WA \vspace{2mm}\\\vspace{1mm}%
	\textsl{Software Engineer} \hfill
	\textbf{June 2013 -- Present}\\
	Moving fast and breaking things.

	\textbf{Microsoft Corporation}, Redmond, WA \vspace{2mm}\\\vspace{1mm}%
	\textsl{Software Development Engineer} \hfill
	\textbf{September 2010 -- May 2013}\\
	Contributed and drove the web experience in a secret Office project that
	pulls together an Azure cloud service, an HTML5 web client and native C++
	desktop client to deliver rich documents.

	\textsl{Software Development Engineer Intern} \hfill
	\textbf{January -- April 2009}\\
	Explored Windows Mobile Win32 API and developed an embedded XAML-based
	network connectivity analyzer utilizing APIs at each network layer.

	\textbf{Broadcom Corporation}, Vancouver, BC \vspace{2mm}\\\vspace{1mm}%
	\textsl{Software Developer Coop} \hfill
	\textbf{May -- August 2008}\\
	Designed software framework component with instant messaging and presence
	functionality for an existing VoIP SIP software stack and administrated SIP,
	presence, and XCAP servers on Debian.

	\textsl{Software Developer Coop} \hfill
	\textbf{May -- December 2007}\\
	Developed a prototype for instant messaging and presence in SIP on VoIP
	enabled cable modems in C/C++, analyzed cryptographic suites and
	optimized the OpenSSL library for embedded device usage, designed and
	programmed a QA infrastructure with Tcl/Tk and Cygwin to enable easy test
	script development and multiple-target testing on a distributed network.

	%----------------------------------
	\section{\mysidestyle Publications}

	Oliver Zheng, Jason Poon, Konstantin Beznosov, ``Application-Based TCP
	Hijacking,'' in Proceedings of the 2009 European Workshop on System
	Security, Nuremberg, Germany, ACM, 31 March 2009

	%----------------------------------------
	\section{\mysidestyle Technical Projects}

	\textbf{Windows Live Messenger Security Analysis} \hfill
	\textbf{September -- December 2007} \vspace{2mm}\\\vspace{1mm}%
	Analyzed Microsoft Notification Protocol (MSNP) used by Windows Live
	Messenger (WLM) and discovered security flaws that could lead to user
	impersonation, developed a technique -- Application-Based TCP Hijacking
	(ABTH) -- that exploits unencrypted TCP/IP protocols including MSNP.

	%-------------------------------
	\section{\mysidestyle Education}

	\textbf{University of British Columbia}
		\textsl{ Vancouver, BC}
		\hfill \textbf{September 2005 -- April 2010}
		\vspace{2mm}\\\vspace{1mm}%
	\textsl{Bachelor of Applied Science, Computer Engineering}
		\vspace{1mm}\\
	Ranked 1st in junior year and 7th in sophmore year out of 220 students

	%-----------------------------------------
	\section{\mysidestyle Honours and\\Awards}

	Trek Excellence Scholarship, 2006 -- 2009
		\vspace{1mm}\\%
	Thomas Beeching Scholarship, 2008
		\vspace{1mm}\\%
	Charles and Jane Banks Scholarship, 2007
		\vspace{1mm}\\%
	President's Entrance Scholarship, 2005
		\vspace{1mm}\\%
	Michael Smith Science Challenge (2nd in BC), 2005

	%----------------------------------------------
	\section{\mysidestyle References}
	References available upon request.

%-----------------------------
%\section{\mysidestyle Referees}
%
%\begin{tabular}{@{}p{6cm}p{6cm}}
%\textbf{Professor Kuldip Paliwal}       &  \textbf{Dr Stephen So}                   \\
%Professor                               &  Associate Lecturer                       \\
%Griffith University                     &  Griffith University                      \\
%Nathan, Queensland, Australia           &  Gold Coast, Queensland, Australia        \\
%phone: \textsl{available on request}    &  phone: \textsl{available on request}     \\
%e-mail: \textsl{available on request}   &  e-mail: \textsl{available on request}    \\
%\end{tabular}
%
%\begin{tabular}{@{}p{6cm}p{6cm}}
%\textbf{Dr Conrad Sanderson}            &  \textbf{Mr Sean Loye}                    \\
%Researcher                              &  Systems Engineer                         \\
%National ICT Australia                  &  Hewlett Packard                          \\
%St Lucia, Queensland, Australia         &  Milton, Queensland, Australia            \\
%phone: \textsl{available on request}    &  phone: \textsl{available on request}     \\
%e-mail: \textsl{available on request}   &  e-mail: \textsl{available on request}    \\
%\end{tabular}

\end{resume}
\end{document}
